A simple and efficient algorithm for computing approximate Nash equilibria in sequential games with imcomplete information

### 2015-07-25 paper.tex
more

\textbf{keywords}: sequential game; incomplete information; perfect
recall; approximate Nash equilibrium; primal-dual
algorithm; convex-optimization

@@

\begin{proof}
It is clear to see that the quadruplet $(\Psi_1, \Psi_2, g_1, g_2)$
satisfies assumptions B.1, B.2, B.3, B.5, and B.6 of
\cite{he2013accelerating} with $L_{xx} = L_{yy} = 0$ and $L_{xy} =
L_{yx} = \|K\|$. Now, one easily computes the proximal operator of
$g_j$ in closed-form as $\prox_{\lambda g_j}(z, v) \equiv ((z)_+,
v - \lambda e_j)$. With all these ingredients in place, Algorithm
\ref{Tab:algo} is then obtained from \cite[Algorithm
  T-BD]{he2013accelerating}, applied on the GSP
\eqref{eq:unconstrained_pb} with the choice of parameters: $\sigma = 1
\in (0, 1]$, $\sigma_x = \sigma_y = 0 \in [0, \sigma)$,
    $\lambda_{xy} := \frac{1}{\sigma L_{xy}}\sqrt{(\sigma^2 -
        \sigma_x^2)(\sigma^2 - \sigma_y^2)} = \sigma / \|K\| =
      1/\|K\|$, and $\lambda = \lambda_{xy} \in (0,
      \lambda_{xy}]$. The convergence result follows immediately from
  \cite[Theorem 4.2]{he2013accelerating}.
\end{proof}

\subsection{Practical considerations}
\paragraph{\textbf{\textit(a) Efficient computation of $Ay$ and $A^Tx$.}}
In Algorithms \ref{Tab:algo}, most of the time is spent
pre-multiplying vectors by $A$ and $A^T$. For \textit{flop-type} poker
games like \textit{Texas Hold'em} and  \textit{Rhode Island Hold'em},
$A$ (and thus $A^T$ too)  is very big (up $10^{100}$ rows and columns!)
but has a rich block-diagnoal structure which can be carefully
exploited, as was done in \cite{hoda2010smoothing}. For the purpose of
completeness, we explain the details of the tricks used in
\cite{hoda2010smoothing} for speeding up the computation of these
matvec products.

>>>>

\textbf{keywords}: algorithmic-game theory; sequential game;
incomplete information; perfect recall; approximate Nash equilibrium;
primal-dual algorithm; convex-optimization

@@

\begin{proof}
It is clear to see that the quadruplet $(\Psi_1, \Psi_2, g_1, g_2)$
satisfies assumptions B.1, B.2, B.3, B.5, and B.6 of
\cite{he2013accelerating} with $L_{xx} = L_{yy} = 0$ and $L_{xy} =
L_{yx} = \|K\|$. Now, one easily computes the proximal operator of
$g_j$ in closed-form as $\prox_{\lambda g_j}(a, b) \equiv ((a)_+,
b - \lambda e_j)$. With all these ingredients in place, Algorithm
\ref{Tab:algo} is then obtained from \cite[Algorithm
  T-BD]{he2013accelerating}, applied on the GSP
\eqref{eq:unconstrained_pb} with the choice of parameters: $\sigma = 1
\in (0, 1]$, $\sigma_x = \sigma_y = 0 \in [0, \sigma)$,
    $\lambda_{xy} := \frac{1}{\sigma L_{xy}}\sqrt{(\sigma^2 -
        \sigma_x^2)(\sigma^2 - \sigma_y^2)} = \sigma / \|K\| =
      1/\|K\|$, and $\lambda = \lambda_{xy} \in (0,
      \lambda_{xy}]$. The convergence result follows immediately from
  \cite[Theorem 4.2]{he2013accelerating}.
\end{proof}

\subsection{Practical considerations}
\paragraph{\textbf{\textit(a) Efficient computation of $Ay$ and $A^Tx$.}}
In Algorithms \ref{Tab:algo}, most of the time is spent
pre-multiplying vectors by $A$ and $A^T$ (precisely 3 such operations
are done per iteration). For \textit{flop-type} poker
games like \textit{Texas Hold'em} and  \textit{Rhode Island Hold'em},
$A$ (and thus $A^T$ too)  is very big (up $10^{14}$ rows and columns!)
but has a rich block-diagnoal structure which can be carefully
exploited, as was done in \cite{hoda2010smoothing}. For the purpose of
completeness, we explain the details of the tricks used in
\cite{hoda2010smoothing} for speeding up the computation of these
matvec products.
